Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-05-08 exp1/iswc2013.tex
htest for fractional
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@528 43ef1190-90fd-4dd7-a769-d0121f02b80e

We then extract two vectors, one for the each of the implementations,
and then perform a one-sided hypothesis test where $H_0$ is that they
are equal and $H_1$ is that the vector representing the new
implementation is smaller. In this example, we find that the available
data supports the assertion that the new implementation is better with a
high probability, $p=2.9 \cdot 10^{-10}$.\todo{rationale could be
  stronger}

@@

\todo{Do t-tests}

>>>>

We then extract two vectors, one for the each of the implementations,
and then perform a one-sided hypothesis test where $H_0$ is that they
are equal and $H_1$ is that the vector representing the new
implementation is smaller. In this example, we find that the available
data supports the assertion that the new implementation is better with a
high probability, $p=2.9 \cdot 10^{-10}$.\todo{rationale could be
  stronger}\todo{figure?}

@@

Since the 64-run experiment also has 3 inactive factors, ``Machine'',
``TripleC'' and ``Range'', we can again treat it as a $2^5$ experiment
replicated twice. Using the same procedure as above, we find that
again, the hypothesis test indicates that the new implementation is an
improvement at $p = 5.9 \cdot 10^{-6}$. The comparatively higher p-value
is due to the lower number of runs. It is also possible to perform the
per-environmental test, but we refrain from that in the interest of
brevity.\todo{good way to say it?}
